Variable Selection

### 2016-05-20 var_select.rmd
regression report

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('RColorBrewer',lib='C:/Progra~1/R/R-3.2.1/library')

@@

```{r, echo=FALSE}
BT.lin<- function(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') {
        formula = paste("return.pdol ~ inv.mlsto + Discipline + client.count + Business +
                              Biz.size + Biz.type + Year + Num.days +
                              no.users + pc.contracttech + client.neginv + client.numinv + client.totinv +
                              pc.director + pc.midtech + pc.midpro + pc.gradpro + pc.seniortech + pc.seniorpro +
                              pc.pro + mean.peeps + hours.perday + num.inv + mean.inv + num.neginv + client.meaninv +
                              code.director + ProjEng.Pos", add.var, sep="+")
        if (type== 'aov') {
            model= aov(as.formula(formula)              
                      ,data= data)
            return(summary(model)) 
        }
        else{
                model=lm(as.formula(formula)                     
                        ,data= data)
                df<- as.data.frame(summary(model)$coefficients)
                df$var<-rownames(summary(model)$coefficients)
                colnames(df)[names(df) %in% 'Pr(>|t|)']<-'Pval'
                return(df %>% arrange(-abs(Estimate)))

@@

# BT.lin(type= 'lm', data= all7a[1:1313,], add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a[1314:2283,], add.var = 'Job.Type.Primary') %>% slice(1:10)
BT.lin(type= 'aov', data= all7a, add.var = 'Job.Type.Primary')
BT.lin(type= 'aov', data= all7a[1314:2283,], add.var = 'Job.Type.Primary')

@@

* Business type
* director code
* Discipline
* Biz.type

@@

write.csv(all7b,'all7b.csv')
all7b<- read.csv('all7b.csv')[,-1]

@@

@@

save(all.cfor2,file= 'C:/Users/n9232371/Documents/Consultbusiness/data/objects/all_cfor2.RData')
# load('C:/Users/n9232371/Documents/github/consult/object/all_cfor2.RData')

@@

rand.rank<- multi.forest1(data=mini.core3, nforest=1:10)

@@

cfor.plotsave<- function(extra= vars, name= 'vare'){
        for(i in 1:length(vars)){

@@

cfor.plotsave(extra=vars, name='vara')
cfor.plotsave(extra=vars, name='varb')
cfor.plotsave(extra=vars, name='varc')
cfor.plotsave(extra=vars, name='vard')
cfor.plotsave(extra=list('majority.pos'), name='vare')

@@

aov.loop<- function(extra=vars.vec){
        for (i in 1:length(extra)){
                core.var= all7c[,names(all7c) %in% c('inv.mlsto', 'timespan', 'no.users', 
                                                     'Discipline', 'pc.pro', 
                        'client.totinv', 'Biz.type','code.director', 'Num.disc', 
                        'Business', 'return.pdol', extra[i])]
                core.var = core.var[!is.na(core.var[,extra[i]]),]

                formula = paste("return.pdol ~ inv.mlsto + Discipline + Business+
                        Biz.type + Num.disc +
                        no.users + 
                        client.totinv + 
                        pc.pro + timespan +
                        code.director", extra[i], sep="+")

                model= aov(as.formula(formula)              
                           ,data= core.var)

                print(extra[i])
                print(model %>% summary)

                cat(i," ")
                }
        }

>>>>

library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('randomForest')
library('RColorBrewer')

@@

```{r, echo=FALSE}
BT.lin<- function(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') {
        formula = paste("return.pdol ~ inv.mlsto + Discipline + client.count + Business +
                              Biz.size + Biz.type + Year + Num.days +
                              no.users + pc.contracttech + client.neginv + client.numinv + client.totinv +
                              pc.director + pc.midtech + pc.midpro + pc.gradpro + pc.seniortech + pc.seniorpro +
                              pc.pro + mean.peeps + hours.perday + num.inv + mean.inv + num.neginv + client.meaninv +
                              code.director + ProjEng.Pos", add.var, sep="+")
        if (type== 'aov') {
            model= aov(as.formula(formula)              
                      , na.action = na.omit, data= data)
            return(summary(model)) 
        }
        else{
                model=lm(as.formula(formula)                     
                        , na.action = na.omit, data= data)
                df<- as.data.frame(summary(model)$coefficients)
                df$var<-rownames(summary(model)$coefficients)
                colnames(df)[names(df) %in% 'Pr(>|t|)']<-'Pval'
                return(df %>% arrange(Pval))

@@

# BT.lin(type= 'lm', data= all7a[1:1313,], add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'lm', data= all7a, add.var = 'Job.Type.Primary') %>% slice(1:20)
BT.lin(type= 'aov', data= all7a, add.var = 'Job.Type.Primary')
BT.lin(type= 'aov', data= all7a, add.var = 'Billing.Type')

#loop to extract p values from anova of all additional variables.

#incomplete variabless:
incomp.vars = c('Post.Code', 'Billing.Type', 'Job.Source', 'Job.Detail.Primary', 'Job.Detail.Secondary', 'Job.Type.Primary',
                'Job.Type.Secondary', 'State', 'Type', 'no.employees', 'contact.count', 'JD.Primary', 'JD.Second', 'dist',
                'timespan', 'Num.disc', 'Inv.freq', 'client.invfreq')
plot.pvals = NULL

for(i in seq_along(incomp.vars)){
        formula = paste("return.pdol ~ inv.mlsto + Discipline + client.count + Business +
                              Biz.size + Biz.type + Year + Num.days +
                              no.users + pc.contracttech + client.neginv + client.numinv + client.totinv +
                              pc.director + pc.midtech + pc.midpro + pc.gradpro + pc.seniortech + pc.seniorpro +
                              pc.pro + mean.peeps + hours.perday + num.inv + mean.inv + num.neginv + client.meaninv +
                              code.director + ProjEng.Pos", incomp.vars[i], sep="+")

        model= aov(as.formula(formula)              
                      , na.action = na.omit, data= data)

        #create columns for results and plotting
        mod.vars = summary(model)[[1]] %>% rownames %>% .[-29]
        mod.vars = sub("\\s+$", "", mod.vars)
        mod.vars = sub(incomp.vars[i], "add.variable", mod.vars)
        p.val = summary(model)[[1]]$'Pr(>F)' %>% .[-29]
        add.variable = rep(incomp.vars[i], 28)

        plot.pvals = rbind(plot.pvals, 
                data.frame(mod.vars, p.val, add.variable)
        )

#order levels in plot.pvals by median
order.vars = ddply(plot.pvals, .(mod.vars), summarise, med = median(p.val))
order.vars = arrange(order.vars, med)
plot.pvals <- within(plot.pvals, 
                         mod.vars <- factor(mod.vars, 
                                               levels=order.vars$mod.vars))
saveRDS(plot.pvals, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/AOV_varimp_plot.rds")

gg <- ggplot(plot.pvals, aes(x = mod.vars, y = p.val)) + geom_boxplot() +
        theme(axis.text.x=element_text(angle=45,hjust=1)) + 
        geom_hline(yintercept = 0.05, colour = 'red', linetype = 2) +
        scale_y_continuous(breaks = c(0,0.05,.25,.5,.75,1)) +
        labs(y = "P value of F statistic", x = "Independent Variables", 
             title = "Summary of P-values from Anova tests")
#which added variable was sgnificant?
plot.pvals %>% filter(p.val <=0.05, mod.vars == "add.variable")
# timespan

@@

* Business type
* director code
* Discipline
* Biz.type
* hours.perday - 0.000455
* code.director - 0.00118
* pc.midtech - 9.11e-07
* no.users = 0.000691
* Num.days = 0.039480

@@

# write.csv(all7b,'all7b.csv')
all7b<- read.csv('all7b.csv')[,-1]

@@

saveRDS(var.imp, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/cfor_varimp.rds")

@@

save(all.cfor2,file= 'C:/Users/n9232371/Documents/Consultbusiness/data/objects/all_cfor2.RData')
load('C:/Users/n9232371/Documents/Consultbusiness/data/objects/all_cfor2.RData')

@@

rand.rank<- multi.forest1(data=mini.core3, nforest=1:10)
rand.rank$var <- sub("inv.mlsto", "Amount Invoiced for Project", rand.rank$var)
rand.rank$var <- sub("no.users", "Number of employees on Project", rand.rank$var)
rand.rank$var <- sub("client.totinv", "Total Amount Invoiced from the Client - Past Jobs", rand.rank$var)
rand.rank$var <- sub("pc.pro", "% of Hours Completed by a Professional-level Employee", rand.rank$var)
rand.rank$var <- sub("Business", "Business Category of Client", rand.rank$var)
rand.rank$var <- sub("client.numinv", "Mean Number of Invoices Submitted to Client - past Jobs", rand.rank$var)
rand.rank$var <- sub("client.meaninv", "Mean Invoice Size for Client - Past Jobs", rand.rank$var)
rand.rank$var <- sub("client.count", "Number of Past Jobs with Client", rand.rank$var)
rand.rank$var <- sub("code.director", "Director", rand.rank$var)
rand.rank$var <- sub("Num.disc", "Number of Internal Disciplines Involved", rand.rank$var)
rand.rank$var <- sub("client.neginv", "Number Bad Debt Client Invoices - Past Jobs", rand.rank$var)
rand.rank$var <- sub("Biz.size", "Client Size in Number of Employees", rand.rank$var)
rand.rank$var <- sub("Biz.type", "Broad Client Business Category (Gov, Private etc)", rand.rank$var)
rand.rank = rename(rand.rank, Variable_Description = var, Rank = m.rank)

saveRDS(rand.rank, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/RF_var_rank.rds")
saveRDS(rand.rank, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/RF_var_rank_subbed.rds")
rand.rank <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/RF_var_rank.rds")
rf.rank <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/RF_var_rank_subbed.rds")

@@

cfor.plotsave<- function(extra= vars, name= 'vare'){
        for(i in 1:length(extra)){

@@

cfor.plotsave(extra=vars, name='vara')
cfor.plotsave(extra=vars, name='varb')
cfor.plotsave(extra=vars, name='varc')
cfor.plotsave(extra=vars, name='vard')
cfor.plotsave(extra=list('majority.pos'), name='vare')
cfor.plotsave(extra=list('pc.majpos'), name='varf')

@@

aov.loop<- function(extra=vars.vec){
        plot.pvals = NULL
        for (i in 1:length(extra)) {
                core.var = all7c[, names(all7c) %in% c('inv.mlsto','timespan','no.users','Discipline',
                                                       'pc.pro','client.totinv','Biz.type',
                                                       'code.director','Num.disc','Business',
                                                       'Biz.size', 'pc.director',
                                                       'return.pdol', extra[i])]

                core.var = core.var[!is.na(core.var[, extra[i]]),]

                formula = paste("return.pdol ~ inv.mlsto + Discipline + Business+Biz.type + Num.disc +
                no.users + client.totinv + pc.pro + timespan + code.director +
                Biz.size + pc.director", extra[i], sep = "+")

                model = aov(as.formula(formula),data = core.var,na.action = na.omit)

                #create columns for results and plotting
                mod.vars = summary(model)[[1]] %>% rownames %>% .[-14]
                mod.vars = sub("\\s+$", "", mod.vars)
                mod.vars = sub(extra[i], "add.variable", mod.vars)
                p.val = summary(model)[[1]]$'Pr(>F)' %>% .[-14]
                add.variable = rep(extra[i], 13)

                plot.pvals = rbind(plot.pvals, data.frame(mod.vars, p.val, add.variable))
        }

        return(plot.pvals)
}

plot.pvals = aov.loop(extra=vars.vec)

#order levels in plot.pvals by median
order.vars = ddply(plot.pvals, .(mod.vars), summarise, med = median(p.val))
order.vars = arrange(order.vars, med)
plot.pvals <- within(plot.pvals, 
                         mod.vars <- factor(mod.vars, 
                                               levels=order.vars$mod.vars))
saveRDS(plot.pvals, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/AOV_varimp_plot.rds")

gg <- ggplot(plot.pvals, aes(x = mod.vars, y = p.val)) + geom_boxplot() +
        theme(axis.text.x=element_text(angle=45,hjust=1)) + 
        geom_hline(yintercept = 0.05, colour = 'red', linetype = 2) +
        scale_y_continuous(breaks = c(0,0.05,.25,.5,.75,1)) +
        labs(y = "P value of F statistic", x = "Independent Variables", 
             title = "Summary of P-values from Anova tests")
#which added variable was sgnificant?
plot.pvals %>% filter(p.val <=0.05, mod.vars == "add.variable")
plot.pvals %>% filter(add.variable == "pc.majpos")
# timespan
